|

### 2023-06-19 paper.Rmd
YAML: change from output: bookdown::pdf_document2 to pdf_document
It is more straightforward and offers the same features (creates a toc, keep_tex, etc).

---
title: |
  |
  | 
  | \vspace{1cm}Writing a reproducible paper
  | in R Markdown^[Corresponding address: mail@paulcbauer.de. Acknowledgments: We are grateful to all those generous people that invest their time into open-source software.]\vspace{0.5cm}
  |
author:
  - Paul Bauer, Mannheim Centre for European Social Research
  - Camille Landesvatter, Mannheim Centre for European Social Research
date: |
  |       
  | First version: December 14, 2018
  | This version: `r gsub("^0", "", format(Sys.time(), "%B %d, %Y"))`
  | Download: https://osf.io/q395s
  |
  | Feedback? Errors? mail@paulcbauer.de
  | [Github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)
  |
  | Tired of Latex?
  | Try [Pagedown](https://github.com/rstudio/pagedown) with our [new template](https://osf.io/k8jhx/)! :-)
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown. Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be downloaded [here](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown) (click on Code -> Download ZIP). We think we got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). We intend to update this file when we discover more convenient code (you can follow any updates through the corresponding [Github repo](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)).\vspace{.8cm}
bibliography: references.bib
csl: american-sociological-association.csl
output:
  bookdown::pdf_document2:
    toc: no
    keep_tex: true
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin=1in
always_allow_html: yes
---

>>>>

---
title: |
  |
  | 
  | \vspace{1cm}Writing a reproducible paper
  | in R Markdown^[Corresponding address: mail@paulcbauer.de. Acknowledgments: We are grateful to all those generous people that invest their time into open-source software.]\vspace{0.5cm}
  |
author:
  - Paul Bauer, Mannheim Centre for European Social Research
  - Camille Landesvatter, Mannheim Centre for European Social Research
date: |
  |       
  | First version: December 14, 2018
  | This version: `r gsub("^0", "", format(Sys.time(), "%B %d, %Y"))`
  | Download: https://osf.io/q395s
  |
  | Feedback? Errors? mail@paulcbauer.de
  | [Github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)
  |
  | Tired of Latex?
  | Try [Pagedown](https://github.com/rstudio/pagedown) with our [new template](https://osf.io/k8jhx/)! :-)
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown. Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be downloaded [here](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown) (click on Code -> Download ZIP). We think we got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). We intend to update this file when we discover more convenient code (you can follow any updates through the corresponding [Github repo](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)).\vspace{.8cm}
bibliography: references.bib
csl: american-sociological-association.csl
output:
  pdf_document:
    toc: no
    keep_tex: true
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin=1in
always_allow_html: yes
---

### 2023-06-19 paper.tex
YAML: change from output: bookdown::pdf_document2 to pdf_document
It is more straightforward and offers the same features (creates a toc, keep_tex, etc).

  \usepackage{unicode-math}

@@

@@

\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}

@@

\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}

@@

\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}

@@

\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}

@@

\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

@@

\setcounter{secnumdepth}{5}

@@

\urlstyle{same} % disable monospaced font for URLs

@@

\title{\hfill\break
\hfill\break
\vspace{1cm}Writing a reproducible paper\\
in R Markdown\footnote{Corresponding address: \href{mailto:mail@paulcbauer.de}{\nolinkurl{mail@paulcbauer.de}}. Acknowledgments: We are grateful to all those generous people that invest their time into open-source software.}\vspace{0.5cm}\\}
\author{Paul Bauer, Mannheim Centre for European Social Research \and Camille Landesvatter, Mannheim Centre for European Social Research}
\date{\hfill\break
First version: December 14, 2018\\
This version: April 05, 2023\\
Download: \url{https://osf.io/q395s}\\
\strut \\
Feedback? Errors? \href{mailto:mail@paulcbauer.de}{\nolinkurl{mail@paulcbauer.de}}\\
\href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github repository}\\
\strut \\
Tired of Latex?\\
Try \href{https://github.com/rstudio/pagedown}{Pagedown} with our \href{https://osf.io/k8jhx/}{new template}! :-)}

@@

To see how referencing works simply see the different examples for figures, tables and sections below. For instance in Section \ref{sec:tables} you can find different ways of referencing tables. The code of the underlying \texttt{paper.rmd} will show you how we referenced Section \ref{sec:tables} right here namely with `\texttt{Section\ \textbackslash{}@ref(sec:tables)}'.

@@

We would recommend to use the command below and simply add it to the appendix as we did here in Appendix \ref{sec:rsessioninfo}. This will make sure you always provide the package versions that you used in the last compilation of your paper. For more advanced tools see \href{https://rstudio.github.io/packrat/}{packrat}.

@@

Table \ref{tab1} shows summary stats of your data.\footnote{To reference the table where you set the identifier in the stargazer function you only need to use the actual label, i.e., ´tab1´.} We normally use \texttt{stargazer()} (\protect\hyperlink{ref-hlavac2013stargazer}{Hlavac 2013}) which offers extreme flexibility regarding table output (see \texttt{?stargazer}).

@@

Table \ref{tab2} shows the output for a regression table. Make sure you name all your models and explicitly refer to model names (M1, M2 etc.) in the text.

@@

Another great function is \texttt{kable()} (\texttt{knitr} package) in combination with \texttt{kableExtra}. Table \ref{tab:tab3} provides an example.\footnote{To reference the table produced by the chunk you need to add ´tab:´ to the chunk name, i.e., ´tab:tab3´.} Again you can modify so many things in both the \texttt{kable()} and the \texttt{kable\_styling()} function. See \href{https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf}{this overview} of all the kable stylings that are possible provided by the package author himself.

@@

Inserting figures can be slightly more complicated. Ideally, we would produce and insert them directly in the \texttt{.rmd} file. It's relatively simple to insert R base graphs as you can see in Figure \ref{fig:fig-1}.

@@

Same is true for ggplot2 as you can see in Figure \ref{fig:fig-2}.

@@

\begin{verbatim}
## R version 4.2.2 (2022-10-31)
## Platform: aarch64-apple-darwin20 (64-bit)
## Running under: macOS Ventura 13.0.1
## 
## Matrix products: default
## BLAS:   /Library/Frameworks/R.framework/Versions/4.2-arm64/Resources/lib/libRblas.0.dylib
## LAPACK: /Library/Frameworks/R.framework/Versions/4.2-arm64/Resources/lib/libRlapack.dylib
## 
## attached base packages:
## [1] stats     graphics  grDevices utils     datasets  methods   base     
## 
## other attached packages:
## [1] ggplot2_3.4.2    kableExtra_1.3.4 knitr_1.42       stargazer_5.2.3 
## 
## loaded via a namespace (and not attached):
##  [1] compiler_4.2.2    pillar_1.9.0      tools_4.2.2       digest_0.6.31    
##  [5] evaluate_0.20     lifecycle_1.0.3   tibble_3.2.1      gtable_0.3.3     
##  [9] viridisLite_0.4.1 pkgconfig_2.0.3   rlang_1.1.0       cli_3.6.1        
## [13] rstudioapi_0.14   yaml_2.3.7        xfun_0.38         fastmap_1.1.1    
## [17] withr_2.5.0       dplyr_1.1.1       httr_1.4.5        stringr_1.5.0    
## [21] xml2_1.3.3        generics_0.1.3    vctrs_0.6.1       systemfonts_1.0.4
## [25] tidyselect_1.2.0  webshot_0.5.4     grid_4.2.2        svglite_2.1.1    
## [29] glue_1.6.2        R6_2.5.1          fansi_1.0.4       rmarkdown_2.21   
## [33] bookdown_0.33     farver_2.1.1      magrittr_2.0.3    scales_1.2.1     
## [37] htmltools_0.5.5   rvest_1.0.3       colorspace_2.1-0  labeling_0.4.2   
## [41] utf8_1.2.3        stringi_1.7.12    munsell_0.5.0
\end{verbatim}

>>>>

  \usepackage{unicode-math} % this also loads fontspec

@@

\ifPDFTeX\else
  % xetex/luatex font selection

@@

\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}

@@

\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}

@@

\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}

@@

\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}

@@

@@

\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

@@

\urlstyle{same}

@@

\title{\hfill\break
\hfill\break
\vspace{1cm}Writing a reproducible paper\\
in R Markdown\footnote{Corresponding address:
  \href{mailto:mail@paulcbauer.de}{\nolinkurl{mail@paulcbauer.de}}.
  Acknowledgments: We are grateful to all those generous people that
  invest their time into open-source software.}\vspace{0.5cm}\\}
\author{Paul Bauer, Mannheim Centre for European Social
Research \and Camille Landesvatter, Mannheim Centre for European Social
Research}
\date{\hfill\break
First version: December 14, 2018\\
This version: June 19, 2023\\
Download: \url{https://osf.io/q395s}\\
\strut \\
Feedback? Errors?
\href{mailto:mail@paulcbauer.de}{\nolinkurl{mail@paulcbauer.de}}\\
\href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github
repository}\\
\strut \\
Tired of Latex?\\
Try \href{https://github.com/rstudio/pagedown}{Pagedown} with our
\href{https://osf.io/k8jhx/}{new template}! :-)}

@@

To see how referencing works simply see the different examples for
figures, tables and sections below. For instance in Section
@ref(sec:tables) you can find different ways of referencing tables. The
code of the underlying \texttt{paper.rmd} will show you how we
referenced Section @ref(sec:tables) right here namely with
`\texttt{Section\ \textbackslash{}@ref(sec:tables)}'.

@@

We would recommend to use the command below and simply add it to the
appendix as we did here in Appendix @ref(sec:rsessioninfo). This will
make sure you always provide the package versions that you used in the
last compilation of your paper. For more advanced tools see
\href{https://rstudio.github.io/packrat/}{packrat}.

@@

Table @ref(tab1) shows summary stats of your data.\footnote{To reference
  the table where you set the identifier in the stargazer function you
  only need to use the actual label, i.e., ´tab1´.} We normally use
\texttt{stargazer()} (\protect\hyperlink{ref-hlavac2013stargazer}{Hlavac
2013}) which offers extreme flexibility regarding table output (see
\texttt{?stargazer}).

@@

Table @ref(tab2) shows the output for a regression table. Make sure you
name all your models and explicitly refer to model names (M1, M2 etc.)
in the text.

@@

Another great function is \texttt{kable()} (\texttt{knitr} package) in
combination with \texttt{kableExtra}. Table @ref(tab:tab3) provides an
example.\footnote{To reference the table produced by the chunk you need
  to add ´tab:´ to the chunk name, i.e., ´tab:tab3´.} Again you can
modify so many things in both the \texttt{kable()} and the
\texttt{kable\_styling()} function. See
\href{https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf}{this
overview} of all the kable stylings that are possible provided by the
package author himself.

@@

Inserting figures can be slightly more complicated. Ideally, we would
produce and insert them directly in the \texttt{.rmd} file. It's
relatively simple to insert R base graphs as you can see in Figure
@ref(fig:fig-1).

@@

Same is true for ggplot2 as you can see in Figure @ref(fig:fig-2).

@@

\begin{verbatim}
## R version 4.2.2 (2022-10-31)
## Platform: aarch64-apple-darwin20 (64-bit)
## Running under: macOS Ventura 13.2.1
## 
## Matrix products: default
## BLAS:   /Library/Frameworks/R.framework/Versions/4.2-arm64/Resources/lib/libRblas.0.dylib
## LAPACK: /Library/Frameworks/R.framework/Versions/4.2-arm64/Resources/lib/libRlapack.dylib
## 
## attached base packages:
## [1] stats     graphics  grDevices utils     datasets  methods   base     
## 
## other attached packages:
## [1] ggplot2_3.4.2         kableExtra_1.3.4.9000 knitr_1.42           
## [4] stargazer_5.2.3      
## 
## loaded via a namespace (and not attached):
##  [1] compiler_4.2.2    pillar_1.9.0      tools_4.2.2       digest_0.6.31    
##  [5] evaluate_0.20     lifecycle_1.0.3   tibble_3.2.1      gtable_0.3.3     
##  [9] viridisLite_0.4.1 pkgconfig_2.0.3   rlang_1.1.0       cli_3.6.1        
## [13] rstudioapi_0.14   yaml_2.3.7        xfun_0.38         fastmap_1.1.1    
## [17] withr_2.5.0       dplyr_1.1.1       httr_1.4.5        stringr_1.5.0    
## [21] xml2_1.3.3        generics_0.1.3    vctrs_0.6.1       systemfonts_1.0.4
## [25] tidyselect_1.2.0  webshot_0.5.4     grid_4.2.2        svglite_2.1.1    
## [29] glue_1.6.2        R6_2.5.1          fansi_1.0.4       rmarkdown_2.21   
## [33] farver_2.1.1      magrittr_2.0.3    scales_1.2.1      htmltools_0.5.5  
## [37] rvest_1.0.3       colorspace_2.1-0  labeling_0.4.2    utf8_1.2.3       
## [41] stringi_1.7.12    munsell_0.5.0
\end{verbatim}
